---
title: "shiny-demo-template"
author: "Awesome Student"
output:
  ioslides_presentation:
    incremental: no
    self-contained: yes
    transition: default
    widescreen: yes
runtime: shiny
---

## Introduction

This document summarizes my own personal explorations of the Shiny package. I have edited the YAML header so that the `author:` field has my name.

## This is the demo app

```{r, echo=FALSE}
shiny.dir <- "shiny-apps/"
shiny.app <- "hello-world"
shinyAppDir(appDir = paste(shiny.dir, shiny.app, sep=""),
  options=list(
    width="100%", height=400
  )
)
```

## Quest 1a: Change the list of names

To create this new app, I copied the `hello-world` directory and app and renamed the copy `hello-world-1a`. 

Then I...*(describe what you did)*

---

```{r, echo=FALSE}
shiny.dir <- "shiny-apps/"
shiny.app <- "hello-world-1a"
shinyAppDir(appDir = paste(shiny.dir, shiny.app, sep=""),
  options=list(
    width="100%", height=400
  )
)
```

## Quest 1b: Change the greeting

To create this new app, I copied the `hello-world-1a` directory and app and renamed the copy `hello-world-1b`. Then... 

---

```{r, echo=FALSE}
shiny.dir <- "shiny-apps/"
shiny.app <- "hello-world-1b"
shinyAppDir(appDir = paste(shiny.dir, shiny.app, sep=""),
  options=list(
    width="100%", height=700
  )
)
```

---

At this point, I decided to commit my changes and push the commit to GitHub.

Then I invited \@rogilmore to collaborate on my work.

## Quest 2

In Quest 2, I have added comments to `shiny-apps/correlation-app/app.R`...

---

```{r, echo=FALSE}
shiny.dir <- "shiny-apps/"
shiny.app <- "correlation-app"
shinyAppDir(appDir = paste(shiny.dir, shiny.app, sep=""),
  options=list(
    width="100%", height=700
  )
)
```

## Quest 3

In Quest 3, I have added comments to `shiny-apps/correlation-app-2/app.R`...

---

```{r, echo=FALSE}
shiny.dir <- "shiny-apps/"
shiny.app <- "correlation-app-2"
shinyAppDir(appDir = paste(shiny.dir, shiny.app, sep=""),
  options=list(
    width="100%", height=700
  )
)
```

## Quest 4

In Quest 4, I changed the styling of my app using Cascading Style Sheets (CSS).
This [site](https://shiny.rstudio.com/articles/css.html) explains how.
Here, I created a `www/` directory under the `correlation-app-2a` folder.
Then, I downloaded a theme (`.css` file) from <https://bootswatch.com/>.
I copied this theme to the `correlation-app-2a/www/` directory.
Finally, I added the theme to the `fluidPage()` call in `app.R`.

I wasn't happy with the stock theme backgrounds, so I created my own file `rog1.css`, set `background-color: #aaa` (a light gray), and then called this file from the `fluidPage()` function in `app.R` using the `includeCSS()` function.

The next page shows the results.

---

```{r, echo=FALSE}
shiny.dir <- "shiny-apps/"
shiny.app <- "correlation-app-2a"
shinyAppDir(appDir = paste(shiny.dir, shiny.app, sep=""),
  options=list(
    width="100%", height=500
  )
)
```

## Quest 5

In Quest 5, I {created my own/modified a Shiny app from <src>}...

```{r, echo=FALSE}
# You will need to uncomment this and edit it for this chunk to run.
# shiny.dir <- "shiny-apps/"
# shiny.app <- "my-shiny-app"
# shinyAppDir(appDir = paste(shiny.dir, shiny.app, sep=""),
#   options=list(
#     width="100%", height=700
#   )
# )
```
